Response to reviewers

### 2025-08-18 paper_plos/reviewer_respose_letter_V1.qmd
additional changes to the draft response letter

Thank you for this point. We've significantly revised the manuscript, focusing on explaining things concisely and ensuring each paragraph is move forward the key points of each section. In summary:

- We've reduced the length of the manuscript from 34 to 28 pages (without references).
- We've removed tangential details and minimized the equations where possible, particularly in the “Early Research” section.
- We've streamlined the manuscript's text--to make each sections purpose more clear. The introductions and conclusions of sections now have a better flow.
- We've removed redundancies where possible, especially in the "Family of Accessibility" section. 
- We've more clearly highlighted the paper's main contribution: namely, a review of the shared origins of spatial interaction modeling and accessibility, how their interpretations have diverged over time, and the introduction of a family of accessibility measures grounded in spatial interaction principles--including total, singly, and doubly constrained cases, as well as variants of “accessible opportunities” and “accessible population".

The key points of the manuscript can be summarised as follows:
- First, it explicitly links accessibility to spatial interaction through their shared intellectual foundations (pre- @hansen1959), highlighting how contemporary accessibility research has diverged and showing the mathematical, intuitive, and interpretative advantages of preserving units through constrained formulations, as done in spatial interaction modeling.
- Second, it introduces 'constraints' to accessibility measures. First: the total constrained accessibility measure as an alternative to the Hansen-type formulation, producing zonal values that represent proportions of the known number of destination masses (i.e., opportunities) or origin masses (i.e., population) in the region. Second: the singly constrained accessibility measure as a competitive method that proportionally allocates opportunities from the destination based on population demand (from the origin), or in the case of market potential, proportional allocation of population from the origin based on the supply of opportunities at the destination. Its per-capita zonal rate is shown to be mathematically equivalent to the widely used two-step floating catchment area (2SFCA) method [@luo2003; @shen1998].

@@

As such, we’ve clarified that the contribution of this work: primarily theoretical and methodological. We’ve also tempered earlier claims about the measure’s real-world applicability, instead allowing readers to consider potential uses and the potential value of reuniting accessibility measures with interpretable units. While we believe these measures utility will be highlighted through real-world examples--we plan to explore these in future publications which make this contribution more practically clear (i.e., where we may have enough space to develop and explore an empirical example without shortchanging the historical context).

>>>>

Thank you for this point. We've significantly revised the manuscript to make it shorter and to ensure we articulate the key points of each section:

- We've substantially reduced the length of the manuscript from 34 to 28 pages (without references).
- We've removed tangential details and minimized the equations where possible, particularly in the “Early Research” section.
- We've streamlined the manuscript's text--to make each sections purpose more clear. The introductions and conclusions of sections now have a better flow.
- We've removed redundancies where possible, especially in the "Family of Accessibility" section. 
- We've more clearly highlighted the paper's main contribution: namely, a review of the shared origins of spatial interaction modeling and accessibility, how their interpretations have diverged over time, and the introduction of a family of accessibility measures grounded in spatial interaction principles.

The key contributions of the manuscript can be summarised as follows:
- First, it explicitly links accessibility to spatial interaction through their shared intellectual foundations (pre- @hansen1959), highlighting how contemporary accessibility research has diverged and showing the mathematical, intuitive, and interpretative advantages of preserving units through constrained formulations, as done in spatial interaction modeling.
- Second, it introduces 'constraints' to accessibility measures grounded in spatial interaction principles.
<!-- First: the total constrained accessibility measure as an alternative to the Hansen-type formulation, producing zonal values that represent proportions of the known number of destination masses (i.e., opportunities) or origin masses (i.e., population) in the region. Second: the singly constrained accessibility measure as a competitive method that proportionally allocates opportunities from the destination based on population demand (from the origin), or in the case of market potential, proportional allocation of population from the origin based on the supply of opportunities at the destination. Its per-capita zonal rate is shown to be mathematically equivalent to the widely used two-step floating catchment area (2SFCA) method [@luo2003; @shen1998].-->

@@

As such, we’ve worked to clarify that the contribution of this work which is primarily theoretical and methodological. We’ve also tempered earlier claims about the measure’s real-world applicability, instead allowing readers to consider potential uses and the potential value of reuniting accessibility measures with interpretable units. While we believe these measures utility would be highlighted through real-world examples--we plan to explore these in future publications which make this contribution more practically clear (i.e., where we may have enough space to develop and explore an empirical example without shortchanging the historical context). In fact, we are currently in conversation with the editor about the possibility to submit a separate paper demonstrating the proposed measures with an empirical case study.
